Rank Verification for Exponential Families

### 2016-08-26 verifying-winner.tex
Typos from major fix fixed

While we aim to declare more candidates to be in the correct order, declaring too many candidates, i.e.\ out-of-place candidates, to be in the right order is undesirable. While it is possible to consider false discovery rate (the expected portion of out-of-place candidates declared) here, we restrict our derivation to FWER (the probability of having out-of-place candidates declared).

@@

Later we will see that Procedure 3 is equivalent to Procedure 3' for the most part, except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.

@@

\begin{proof}
We will first show that Procedure 3' falls into the sequential goodness-of-fit testing framework proposed by \citet{Fithian:2015uj}. We thus analyze Procedure 3' as a special case of the BasicStop procedure on random hypothesis, described in the same paper. This enables us to construct valid selective $p$-values and derives Procedure 3'.

@@

While impractical, Procedure 3' can be thought of as performing all $n$ tests first, producing a sequence of $p$-values $p_j$, returning
\begin{equation}
\hat{j}_0 = \min\left\{j: p_j > \alpha\right\} - 1.
\label{eq:basicstop}
\end{equation}
This is a special case of the BasicStop procedure. Instead simply checking that Procedure 3' fits all the requirement for FWER control in BasicStop, we will give the construction of Procedure 3', assuming that we are to estimate $j_0$ with BasicStop.

@@

\paragraph{Construction of $p$-values}

@@

As a brief summary, we want to construct $p$-values $p_j$ such that
$$\PP_{\substack{\theta_{\tau_1} > \cdots > \theta_{\tau_j} \\ \theta_{\tau_j} \le \max_{k>j} \theta_{\tau_k}}} \left[p_j \le \alpha \;\middle|\; X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right].$$
To avoid the clutter in the subscript notation, we will drop the $\tau$ in the subscript. Hence our goal is now
$$\PP_{\substack{\theta_1 > \cdots > \theta_j \\ \theta_j \le \max_{k>j} \theta_k}} \left[p_j \le \alpha \;\middle|\; X_1 \ge \cdots \ge X_j \ge \max_{k>j} X_k\right]$$
Construction of $p_j$ for other permutations $\tau$ can be obtained similarly.

@@

It is not necessarily true that $X_{j+1} = \max_{\ell > j} X_\ell$, but we will use so as a shorthand and simplify our notation. Now the $p$-values are similar to the ones in \Cref{eq:p1j} for $k>j$.

@@

We can graphically represent this in a diagram (\Cref{fig:croprays}) similar to \Cref{fig:comparerays}.

@@

Upon constructing $p_j$, one should realize that the $p$-values for testing $\theta_k \le \theta_{k+1}$ would have been constructed in earlier iterations of BasicStop. In other words, $p_j = \max_{k \le j} p_k'$ is the sequence of $p$-values that works with BasicStop. However, from \eqref{eq:basicstop},
$$\hat{j}_0 = \min\left\{j: \max_{k \le j} p_k' > \alpha\right\} - 1 = \min\left\{j: p_j' > \alpha\right\} - 1,$$
so it is safe to apply BasicStop to $p_j'$ directly, yielding Procedure 3'.

>>>>

While we aim to declare more candidates to be in the correct order, declaring too many candidates, i.e.\ out-of-place candidates, to be in the right order is undesirable. It is possible to consider false discovery rate (the expected portion of out-of-place candidates declared) here, but we restrict our derivation to FWER (the probability of having any out-of-place candidates declared).

@@

Procedure 3 is equivalent to Procedure 3' for the most part, except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.

@@

\begin{proof}
We will first show that Procedure 3' falls into the sequential goodness-of-fit testing framework proposed by \citet{Fithian:2015uj}. We thus analyze Procedure 3' as a special case of the BasicStop procedure on random hypothesis, described in the same paper. This enables us to construct valid selective $p$-values and derive Procedure 3'.

@@

While impractical, Procedure 3' can be thought of as performing all $n$ tests first, producing a sequence of $p$-values $p_j$, and returning
\begin{equation}
\hat{j}_0 = \min\left\{j: p_j > \alpha\right\} - 1.
\label{eq:basicstop}
\end{equation}
This is a special case of the BasicStop procedure. Instead of simply checking that Procedure 3' fits all the requirement for FWER control in BasicStop, we will give the construction of Procedure 3', assuming that we are to estimate $j_0$ with BasicStop.

@@

\paragraph{Considerations for conditioning}

@@

As a brief summary, we want to construct $p$-values $p_j$ such that
$$\PP_{\substack{\theta_{\tau_1} > \cdots > \theta_{\tau_j} \\ \theta_{\tau_j} \le \max_{k>j} \theta_{\tau_k}}} \left[p_j \le \alpha \;\middle|\; X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right].$$

\paragraph{Construction of the $p$-values}

To avoid the clutter in the subscript notation, we will drop the $\tau$ in the subscript. Hence our goal is now
$$\PP_{\substack{\theta_1 > \cdots > \theta_j \\ \theta_j \le \max_{k>j} \theta_k}} \left[p_j \le \alpha \;\middle|\; X_1 \ge \cdots \ge X_j \ge \max_{k>j} X_k\right]$$
Construction of $p_j$ for other permutations $\tau$ can be obtained similarly.

@@

It is not necessarily true that $X_{j+1} = \max_{\ell > j} X_\ell$, but we will use so as a shorthand and simplify our notation. Now the $p$-values are similar to the ones in \Cref{eq:p1j}, for $k>j$:

@@

We can graphically represent $p_{jk}$ in \Cref{fig:croprays}, a diagram analogous to \Cref{fig:comparerays}.

@@

Upon constructing $p_j$, one should realize that the $p$-values for testing $\theta_k \le \theta_{k+1}$ would have been constructed in earlier iterations of BasicStop, as $p_k'$. In other words, $p_j = \max_{k \le j} p_k'$ is the sequence of $p$-values that works with BasicStop. However, from \eqref{eq:basicstop},
$$\hat{j}_0 = \min\left\{j: \max_{k \le j} p_k' > \alpha\right\} - 1 = \min\left\{j: p_j' > \alpha\right\} - 1,$$
so it is safe to apply BasicStop to $p_j'$ directly, yielding Procedure 3'.
\end{proof}
